Hydras \& Co.

### 2022-09-07 doc/chapter-encoding.tex
work on the  chapter on goedel encodings

>>>>

       \subsection{List encoding}

       The encoding of a list of natural numbers is based
       on \texttt{cPair}, through a structural recursion.

       \inputsnippets{cPair/codeListDef}

       Let us look at the main step of the proof that \texttt{codeList} is injective.

  \inputsnippets{cPair/codeListInj}
  \inputsnippets{cPair/codeListInja}

  Applying \texttt{cPair}'s injectivity  and the induction hypothesis allows us to complete the proof.

  \subsubsection{Encoding the \texttt{nth} function}

  The following function allows us to compute the $n$-th element of a list of natural numbers, \emph{directly on the encoding of the considered list}.

  In the current version of the Ackermann Library, this function is defined \emph{via} an interactive proof. Its specification and
  correctness are proved by  separate lemmas.

  \inputsnippets{cPair/codeNthDef}
  \inputsnippets{cPair/codeNthCorrect}
   \inputsnippets{cPair/codeNthIsPR}

  \begin{exercise}
  Give a new equivalent definition of \texttt{codeNth}, without using tactics like \texttt{assert}.  You may define an help function for this purpose, in which case, please specify what your helper computes.
  \end{exercise}
